Stochastic Approximation Monte Carlo with a Dynamic Update Factor (SAD)

### 2019-02-11 papers/histogram/sad.tex
a few more davidsays in the paper

%\begin{figure}
  %\includegraphics[width=\columnwidth]{figs/gamma-n500}
  %\caption{The update factor $\gamma_t$ for $N=500$ versus iteration for three
    %different methods: WL, SAMC, and SAD.
    %method.}\label{fig:gamma-vs-t}
%\end{figure}
\begin{figure}
  \includegraphics[width=\columnwidth]{figs/gamma-n50}
  \caption{The update factor $\gamma_t$ for $N=50$ versus iteration for three
    different methods: WL, SAMC, and SAD.}
\end{figure}

\paragraph{Energy binning with SAD}

@@

@@

\begin{figure}
\includegraphics[width=\columnwidth]{figs/s000/periodic-ww1_50-ff0_17-N256-entropy-error-default.pdf}
  \caption{The average entropy error for each MC method is shown for $\eta = 0.17$ and $T_{\min} = 1$ with
  SAD serving as the reference.}\label{fig:n256}
\end{figure}
%\begin{figure}
%\includegraphics[width=\columnwidth]{figs/s000/periodic-ww1_30-ff0_30-N500-entropy-error-default.pdf}
  %\caption{The average entropy error for each MC method is shown for $\eta = 0.3$ and $T_{\min} = 1/2$ with
  %SAMC $t_0 = 10^6$ serving as the reference.}\label{fig:n500-ff0.3}
%\end{figure}
\begin{figure}
  \includegraphics[width=\columnwidth]{figs/N256-lndos-comparison}
  \caption{Use this to create description of the system.}\label{fig:n256-lndos-comparison}
\end{figure}

@@

>>>>

%\begin{figure}
  %\includegraphics[width=\columnwidth]{figs/gamma-n500}
  %\caption{The update factor $\gamma_t$ for $N=500$ versus iteration for three
    %different methods: WL, SAMC, and SAD.
    %method.}\label{fig:gamma-vs-t}
%\end{figure}
\paragraph{Energy binning with SAD}

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{figs/gamma-n50}
  \caption{\davidsays{We need to make a distinction between SAD and
      SAD both in figure and in caption.  I don't know what to call
      the slow SAD.  Also, should this move down to results, and do we
      want slow WL and slow-1/t WL?} The update factor $\gamma_t$ for
    $N=50$ versus iteration for three different methods: WL, SAMC, and
    SAD.}\label{fig:fast-slow-gamma}
\end{figure}

@@

To see how SAD, WL, and $1/t$-WL compensate for the smaller
displacement distance, \davidsays{see Fig.~\ref{fig:fast-slow-gamma}
  and discuss this}

\begin{figure}
\includegraphics[width=\columnwidth]{figs/s000/periodic-ww1_50-ff0_17-N256-entropy-error-default.pdf}
  \caption{The average entropy error for each MC method is shown for $\eta = 0.17$ and $T_{\min} = 1$ with
  SAD serving as the reference.}\label{fig:n256}
\end{figure}
%\begin{figure}
%\includegraphics[width=\columnwidth]{figs/s000/periodic-ww1_30-ff0_30-N500-entropy-error-default.pdf}
  %\caption{The average entropy error for each MC method is shown for $\eta = 0.3$ and $T_{\min} = 1/2$ with
  %SAMC $t_0 = 10^6$ serving as the reference.}\label{fig:n500-ff0.3}
%\end{figure}
\begin{figure}
  \includegraphics[width=\columnwidth]{figs/N256-lndos-comparison}
  \caption{\davidsays{This could be prettier, and do we need it? We
      definitely need a caption if we keep it.} Use this to create
    description of the system.}\label{fig:n256-lndos-comparison}
\end{figure}

@@

\davidsays{Make this section match the previous one.}
